---
title: CV -- Haziq Jamil
description: Curriculum vitae for Dr Haziq Jamil, Assistant Professor in Statistics (UBD).
output:
  pagedown::html_paged:
    title: Haziq
    css: ["css/one-column-paged-academic.css", "css/font-awesome-5.1.0/css/all.css"]
    number_sections: false
links-to-footnotes: true
# knit: pagedown::chrome_print
params:
  pdf_mode:
    value: false
---

```{r setup, include = FALSE}
# Libraries
library(tidyverse)
library(knitr)
library(lubridate)
library(glue)

# knitr options
knitr::opts_chunk$set(echo = FALSE, warning = FALSE, message = FALSE)

## ---- Helper functions -------------------------------------------------------

# function which takes a name and replaces the first name with initial and dot
replace_first_name_with_initial_and_dot <- function(author_name) {
  str_replace(author_name, "(?<=\\S)\\S+", "\\.")
}

# function for doing this for an entry with a number of authors
replace_first_names_in_list_with_initial_and_dot <- function(authors) {
  authors_split <- str_split(authors, ",") %>% 
    map(str_trim)
  
  authors_split[[1]] %>% map_chr(replace_first_name_with_initial_and_dot) %>% 
    paste0(collapse = ", ")
}

# function for adding leading zero's when there's more than 10 entries
padding_function <- function(cv_entries_tibble, letter_to_pad) {
  if (nrow(cv_entries_tibble) > 9) {
    cv_entries_tibble %>% 
      arrange(date) %>%
      mutate(number = str_pad(row_number(), width = 2, side = "left", pad = "0"),
             number = str_c(letter_to_pad, number)) %>%
      arrange(desc(date))
  } else {
    cv_entries_tibble %>% 
      arrange(date) %>%
      mutate(number = str_pad(row_number(), width = 1, side = "left", pad = "0"),
             number = str_c(letter_to_pad, number)) %>%
      arrange(desc(date))
  }
}

# function for making a year blank when it's the same as the one preceding it
blank_year_when_repeated <- function(cv_entry_tibble){
  cv_entry_tibble %>% 
    mutate(row_number = row_number()) %>% 
    mutate(year = as.character(year),
           year = case_when(
             row_number == 1 ~ year,
             year == lag(year) ~ "",
             year != lag(year) ~ year
           ))
}


## ---- Read data --------------------------------------------------------------
source("_content/sync_w_gsheets.R")  # read data

# Publications
publications <- 
  read_csv("_content/publications.csv") %>% 
  mutate(authors_full = map_chr(authors_full, 
                                replace_first_names_in_list_with_initial_and_dot)) %>% 
  mutate(authors_full = str_replace(authors_full, "H\\. Jamil", "*H\\. Jamil*")) %>%  # Make my name italic
  mutate(year = year(date))

# CV entries
cv_entries <- read_csv("_content/cv_entries.csv") %>% 
  mutate(year = year(date)) %>%
  mutate(year_end = case_when(
    date_end == "present" ~ date_end,
    !is.na(date_end) ~ str_sub(date_end, 1, 4),
    is.na(date_end) ~ date_end
  )) %>%
  mutate(year = ifelse((is.na(year_end) | year == year_end),
                      year,
                      str_c(year, " --- ", year_end)))

# Rename pdf file
if (file.exists("index.pdf")) {
  if (file.exists("haziq_cv.pdf")) file.remove("haziq_cv.pdf")
  file.rename(from = "index.pdf", "haziq_cv.pdf")
}
```

:::::: {.title-and-contact}

::: {.title}
<h1 class="title">Haziq Jamil</h1>
:::

::: {.contact-info}
haziq.jamil@ubd.edu.bn <i class="fas fa-fw fa-envelope"></i>
https://haziqj.ml <i class="fas fa-fw fa-globe-asia"></i>
:::

::::::

:::::: {.research-interests}

::: {.mylink}
```{r cv_logo, out.width = "80%", fig.height = 4.1 / 1.35, fig.width = 2.5 / 1.35}
source("cv_logo.R")
if (isTRUE(params$pdf_mode)) {
  p.static
} else {
  # This takes a long time to animate!
  p.anim
}
```

```{r download_view, results = "asis"}
if(params$pdf_mode){
  cat("<i class='fas fa-fw fa-globe-asia'></i> View this CV online at *haziqj.ml/cv*")
} else {
  cat("<a href='https://haziqj.ml/cv/haziq_cv.pdf'><i class='fas fa-fw fa-download'></i> Download a PDF of this CV</a>")
}
```
:::

::: {.interests}
I am an **Assistant Professor in Statistics** at _Universiti Brunei Darussalam_ (UBD).
My expertise lie in statistical methodology and computation, with applications towards the natural and social sciences.

I am passionate about bringing data and technology to the forefront of our daily interaction with the world.
Using the R programming language, I build statistical models to analyse data to gain insights, make predictions, and aid decision-making.
I am constantly engaged in cross-disciplinary research collaborations and statistical consultations.


<h5>Research Interests</h5>

|                                      |        |                               |
|--------------------------------------|--------|-------------------------------|
| Latent variable models               | &nbsp;&nbsp;&nbsp; | Structural equation models    |
| Binary and multinomial probit models | &nbsp;&nbsp;&nbsp; | Truncated normal distribution |
| Bayesian estimation                  | &nbsp;&nbsp;&nbsp; | EM algorithms                 |
| Variational inference                | &nbsp;&nbsp;&nbsp; |                               |

:::
::::::

<div class="cv-entries">

## Education
```{r}
cv_entries %>% 
  filter(type == 'education') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}<br>", 
                      "{additional_info}<br>",
                      "<span class='cv-entry-gray'>{additional_info2}</span>")) %>% 
  select(year, what) %>%
  mutate(what = gsub("NA", "", what)) %>%
  kable()
```

## Awards & honours
```{r}
cv_entries %>% 
  filter(type == 'awards') %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span>, {where}")) %>%  
  blank_year_when_repeated() %>% 
  select(year, what) %>%
  kable()
```

<br>

## Experience
```{r}
cv_entries %>% 
  filter(type == 'experience', is.na(exclude)) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{what}</span><br>",
                     "{where}<br>", "<span class='cv-entry-gray'>{additional_info}</span>")) %>% 
  select(year, what) %>% 
  kable()
```

## Service
```{r}
cv_entries %>% 
  filter(type == 'service', is.na(exclude)) %>% 
  mutate(what = ifelse(
    is.na(additional_info),
     glue("<span class='cv-entry-title'>{what}</span><br>{where}<br>"),
     glue("<span class='cv-entry-title'>{what}</span><br>",
          "{where}<br>", "<span class='cv-entry-gray'>{additional_info}</span>")
  )) %>%
  select(year, what) %>% 
  kable()
```

## Consultancy
```{r}
cv_entries %>% 
  filter(type == 'consultancy', is.na(exclude)) %>% 
  mutate(what = ifelse(
    is.na(additional_info),
     glue("<span class='cv-entry-title'>{what}</span><br>{where}<br>"),
     glue("<span class='cv-entry-title'>{what}</span><br>",
          "{where}<br>", "<span class='cv-entry-gray'>{additional_info}</span>")
  )) %>%
  select(year, what) %>% 
  kable()
```

## Grants and funding
```{r}
cv_entries %>%
  filter(type == 'major_grants') %>%
  mutate(what = if_else(
    is.na(additional_info),
    glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}"),
    glue("<span class='cv-entry-title'>{what}</span> ({additional_info2}), {where}.<br>", 
         "<span class='cv-entry-gray'>{additional_info}</span>")
  )) %>%
  select(year, what) %>%
  kable()
```


## Publications {.three-split}

<!-- :::::: {.grid-container-publications} -->
<!-- ::: {.conference-publication-heading} -->
<!-- <h3>Conference publications <br><span class="review-note">(fully reviewed, archival)</span></h3> -->
<!-- ::: -->
<!-- ::: {.conference-note} -->
<!-- <h3>In computer science, top-tier conferences (<30% acceptance rate) are as, or more impactful than journals, see doi.org/fgjt2h</h3> -->
<!-- ::: -->
<!-- :::::: -->

<h3>Articles <span class="review-note">(peer-reviewed)</span></h3>

```{r}
publications %>%
  filter(type == "paper") %>% 
  # insert appropriate icon for paper awards (and start with a line break)
  mutate(award = case_when(
    !is.na(award) & str_detect(award, "honourable") ~ glue("<br><i class='fas fa-fw fa-award'></i> <span class='publication-award'>{award}</span>"),
    !is.na(award) ~ glue("<br><i class='fa fa-fw fa-trophy'></i> <span class='publication-award'>{award}</span>"),
    TRUE ~ ""
  )) %>% 
  # create citations
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue}</span>{award}")) %>% 
                         # "<span class='publication-venue'>{venue_abbrev}: {venue}</span>{award}")) %>% 
  # number entries with a prefix
  padding_function(., "A") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, citation) %>%
  knitr::kable()
```

<!-- <br class="pageBreak"> -->
<h3>Working papers <span class="review-note">(preprints and unpublished reports)</span></h3>

```{r}
publications %>%
  filter(type == "preprint") %>% 
  mutate(citation = ifelse(
    is.na(venue), 
    glue("<span class='cv-entry-title'>{title}</span><br>",
         "<span class='publication-authors'>{authors_full}</span><br>"),
    glue("<span class='cv-entry-title'>{title}</span><br>",
         "<span class='publication-authors'>{authors_full}</span><br>",
         "<span class='publication-venue'>{venue}</span>")
  )) %>% 
  padding_function(., "W") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()
```

<h3>Software</h3>

```{r}
publications %>%
  filter(type == "software") %>% 
  mutate(citation = glue("<span class='cv-entry-title'>{title}</span><br>",
                         "<span class='publication-authors'>{authors_full}</span><br>",
                         "<span class='publication-venue'>{venue}</span>")) %>%
  padding_function(., "S") %>% 
  blank_year_when_repeated() %>%
  select(year, number, citation) %>%
  knitr::kable()
```

## Research dissemination

### Posters and short presentations {.three-split}
```{r}
cv_entries %>% 
  filter(type == 'poster', is.na(exclude)) %>% 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) %>%
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) %>% 
  padding_function(., "P") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()
```

### Talks {.three-split}

::: {.conference-presentations-omitted}
Further information for the following talks are available at  <span class='mylink'><a href='https://github.com/haziqj/cv'> haziqj.ml/talk </a></span>
:::

```{r}
cv_entries %>% 
  filter(type == 'talk', is.na(exclude)) %>% 
  # add commas as appropriate
  mutate(where = if_else(!is.na(where) & !is.na(institution), glue(", {where}"), where),
         department = if_else(!is.na(department), glue(", {department}"), department),
         slides = if_else(!is.na(slides), glue("<a href={slides}>Slides</a>"), ""),
         video = if_else(!is.na(video), glue("<a href={video}>Video</a>"), "")) %>%
  mutate(additional_info = if_else(!is.na(additional_info), glue(", {additional_info}"), "")) %>% 
  mutate(what = glue("<span class='cv-entry-title'>{institution}{where}</span>{department}{additional_info}<br>",
                      "<span style='display:inline-block;' class='talk-title'>{what}</span>", 
                     .na = "")) %>% 
  padding_function(., "T") %>% 
  blank_year_when_repeated() %>% 
  select(year, number, what) %>% 
  knitr::kable()
```

## Skills

:::::: {.research-interests}

::: {.spacer}
:::

::: {.interests}
<i class='fas fa-fw fa-chart-line'></i> &nbsp; **Programming, data analysis and visualisation** using R, BUGS/JAGS, Stan, Stata, Mplus, and Mathematica

<i class='fa fa-fw fa-flask'></i> &nbsp; **Reproducible research** using R Markdown, LaTeX, Git and AWS EC2

<i class='fa fa-fw fa-laptop'></i> &nbsp; **Web development** using HTML, Hugo, Jekyll, GitHub Pages and Netlify
:::

::::::

<!-- close 'cv-entries' div -->
</div>

<br class="pageBreak">

The source code for this document is available from <span class='mylink'><a href='https://github.com/haziqj/cv'> github.com/haziqj/cv </a></span>

# Links
